\documentclass[handout]{ximera}

\input{../../preamble.tex}

\title[Dig-In:]{Applications of integrals}
\begin{document}
	\begin{abstract}
		We give more contexts to understand integrals.
	\end{abstract}
	\maketitle
	
	Conceptualizing definite integrals as ``signed area'' works great as
	long as one can actually visualize the ``area.'' In some cases, a
	better metaphor for integrals comes from the idea of \textit{average
		value}.  Looking back to your days as an even younger mathematician,
	you may recall the idea of an \textit{average}:
	\[
	\frac{f_1+f_2+\dots+f_n}{n} = \frac{1}{n}\sum_{k=1}^n f_i
	\]
	If we want to know the average value of a function, a naive approach
	might be to partition the interval $[a,b]$ into $n$ equally spaced
	subintervals, 
	\[
	a=x_0 < x_1 < \dots < x_{n}=b
	\]
	and choose any $x_k^*$ in $[x_i,x_{i+1}]$. The average of $f(x_1^*)$,
	$f(x_2^*)$, \dots, $f(x_n^*)$ is:
	\[
	\frac{f(x_1^*) + f(x_2^*) + \dots + f(x_n^*)}{n} = \frac1n\sum_{k=1}^n f(x_k^*).
	\]
	Multiply this last expression by $1 = \frac{(b-a)}{(b-a)}$:
	\begin{align*}
	\frac1n \sum_{k=1}^n f(x_k^*)\frac{(b-a)}{(b-a)} &= \sum_{k=1}^n f(x_k^*)\frac1n \frac{(b-a)}{(b-a)} \\
	&= \frac{1}{b-a} \sum_{k=1}^n f(x_k^*)\frac{b-a}n  \\
	&=\frac{1}{b-a} \sum_{k=1}^n f(x_k^*)\Delta x
	\end{align*}
	where $\Delta x = (b-a)/n$.  Ah! On the right we have a Riemann Sum!
	Now take the limit as $n\to\infty$:
	\[
	\lim_{n\to\infty} \frac{1}{b-a} \sum_{k=1}^n f(x_k^*)\Delta x = \frac{1}{b-a} \int_a^b f(x)\d x.
	\]
	This leads us to our next definition:
	
	\begin{definition}
		Let $f$ be continuous on $[a,b]$. The \dfn{average value} of $f$ on
		$[a,b]$ is given by
		\[
		\frac{1}{b-a}\int_a^b f(x)\d x.
		\]
	\end{definition}
	
	The average value of a function gives the height of a single rectangle whose area is equal to
	\[
	\int_a^b f(x) \d x
	\]
	\begin{image}
		\begin{tikzpicture}[
		declare function = {f(\x) = -sin(deg(\x)) + 3;}]
		\begin{axis}[  
		domain=-.2:7, xmin =-.2,xmax=7,ymax=5,ymin=-.7,
		width=6in,
		height=3in,xtick={1,6},
		xticklabels={$a$,$b$},
		ytick style={draw=none},
		yticklabels={},
		axis lines=center, xlabel=$x$, ylabel=$y$,
		every axis y label/.style={at=(current axis.above origin),anchor=south},
		every axis x label/.style={at=(current axis.right of origin),anchor=west},
		axis on top,
		]
		\foreach \rectnumber in {1}
		{
			\addplot [draw=penColor,fill=fillp] plot coordinates
			{({1+(\rectnumber - 1) * 5},{3.08})
				({1+(\rectnumber) * 5},{3.08})} \closedcycle;
		};
		\addplot [very thick,penColor, smooth] {f(x)};
		\node[black] at (axis cs:3.5,1.5) {\huge$\int_a^b f(x) \d x$};
		\end{axis}
		\end{tikzpicture}
	\end{image}
	
	An application of this definition is given in the next example.
	
	
	\begin{example}
		An object moves back and forth along a straight line with a velocity
		given by $v(t) = (t-1)^2$ on $[0,3]$, where $t$ is measured in seconds
		and $v(t)$ is measured in ft/s.
		
		What is the average velocity of the object?


\newpage
	\end{example}
	
	
	
	When we take the average of a finite set of values, it does not matter
	how we order those values.  When we are taking the average value of a
	function, however, we need to be more careful.
	
	For instance, there are at least two different ways to make sense of a
	vague phrase like ``The average height of a point on the unit semi
	circle''
	\begin{image}
		\begin{tikzpicture}[
		declare function = {f(\x) = sin(deg(\x));}]
		\begin{axis}[  
		domain=-3:3, xmin =-1.2,xmax=1.2,ymax=1.2,ymin=-.2,
		width=6in,
		height=3in,xtick={-1,1},
		xticklabels={$-1$, $1$},
		ytick style={draw=none},
		yticklabels={},
		axis lines=center, xlabel=$x$, ylabel=$y$,
		every axis y label/.style={at=(current axis.above origin),anchor=south},
		every axis x label/.style={at=(current axis.right of origin),anchor=west},
		axis on top,
		]
		\addplot [penColor, very thick, smooth, domain=(0:180)] ({cos(x)},{sin(x)});
		\end{axis}
		\end{tikzpicture}
	\end{image}


\begin{example}	One way we can make sense of ``The average height of a point on the
	unit semi circle'' is to compute the average value of the function
	\[
	f(x) =\sqrt{1-x^2}
	\]
	on the interval $[-1,1]$.
	
\newpage
	
\end{example}

\begin{example}
	Another way we can make sense of ``The average height of a point on the
	unit semi circle'' is the average value of the function
	\[
	g(\theta) =\sin(\theta)
	\]
	on $[0,\pi]$, since $\sin(\theta)$ is the height of the point on the
	unit circle at the angle $\theta$.
	
		See if you can understand intuitively why the average using $f$ should
		be larger than the average using $g$.

\newpage

	\end{example}
	
  %% It is amusing to note that
	%% since
	%% \[
	%% g(x) < f(x)
	%% \]this
	%% shows that $\pi^2>8$.
	
	
	
	\section{Mean value theorem for integrals}
	
	Just as we have a Mean Value Theorem for Derivatives, we also have a
	Mean Value Theorem for Integrals.
	
	
	\begin{theorem}[The Mean Value Theorem for integrals]\index{Mean Value Theorem for integrals}
		Let $f$ be continuous on $[a,b]$. There exists a value $c$ in $[a,b]$
		such that
		\[
		\int_a^bf(x)\d x = f(c)(b-a).
		\]
	\end{theorem}
	
	This is an \emph{existential} statement. The Mean Value Theorem for
	Integrals tells us:
	\begin{quote}
		\textbf{The average value of a continuous function is in the range of
			the function.}
	\end{quote}
	
	We demonstrate the principles involved in this version of the Mean
	Value Theorem in the following example.
	
	\begin{example}%%%BADBAD we state that this is an existential thm, then we ask for the value!
		Consider $\int_0^\pi \sin x \d x$. Find a value $c$ guaranteed by the Mean Value Theorem.
		
		\vspace{1.7 in}
	
			A graph of $\sin x$ is sketched along with a rectangle with height
			$\sin (0.69)$ are pictured below. The area of the rectangle is the
			same as the area under $\sin x$ on $[0,\pi]$.
			\begin{image}
				\begin{tikzpicture}[
				declare function = {f(\x) = sin(deg(\x));}]
				\begin{axis}[  
				domain=-.2:3.3, xmin =-.2,xmax=3.3,ymax=1.2,ymin=-.2,
				width=6in,
				height=3in,xtick={3.141,6.282},
				xticklabels={$\pi$, $2\pi$},
				ytick style={draw=none},
				yticklabels={},
				axis lines=center, xlabel=$x$, ylabel=$y$,
				every axis y label/.style={at=(current axis.above origin),anchor=south},
				every axis x label/.style={at=(current axis.right of origin),anchor=west},
				axis on top,
				]
				\addplot [draw=penColor,fill=fillp] plot coordinates
				{({0},{2/pi})
					({pi},{2/pi})} \closedcycle;
				\addplot [very thick,penColor, smooth] {f(x)};
				
				\end{axis}
				\end{tikzpicture}
			\end{image}
	\end{example}
\end{document}